Nested sampling with two objective functions

### 2016-02-09 Paper/ms.tex
Condition on lambda

The prior for the pixel intensities $\{m_i\}$ has an ``entropic'' form,
where images are upweighted (relative to a uniform prior) if the pixel
intensities have a low dynamic range. The prior density is
\begin{eqnarray}
p(\boldsymbol{m}) \propto \exp
\left[
-\lambda \sum_{i=1}^n m_i \ln m_i
\right]
\end{eqnarray}
where $\lambda$ is a hyperparameter.

In the 1980s, this prior was thought to have a fundamental status, but this
is no longer the case \citep{massinf}. Instead, we can consider the configurational
entropy $-\sum_{i=1}^n m_i \ln m_i$ as simply a function of an image that may
be relevant somehow, and that we are uncertain about.

The posterior for the underlying image given the data is
\begin{eqnarray}
p(\boldsymbol{m} | \boldsymbol{D})
&=& \frac{p(\boldsymbol{m})p(\boldsymbol{D}|\boldsymbol{m})}
{\int p(\boldsymbol{m})p(\boldsymbol{D}|\boldsymbol{m}) \,d^n\boldsymbol{m}}\\
&=& \frac{\exp\left[-\lambda \sum_i m_i\ln m_i
-\frac{1}{2\sigma^2}\left(D_i - \sum_{j} P_{ij}m_{j}\right)^2\right]}
{\int \exp\left[-\lambda \sum_i m_i\ln m_i
-\frac{1}{2\sigma^2}\left(D_i - \sum_{j} P_{ij}m_{j}\right)^2\right]\, d^n\boldsymbol{m}}
\end{eqnarray}

Therefore, this is a `doubly intractable' problem \citep{murray}. An integral, whose
result is a function of the parameters, appears in the {\em denominator} of the
target density. However, in our case the integral in the
denominator arises from the prior for the parameters, rather than from the
likelihood function.

>>>>

The prior for the pixel intensities $\{m_i\}$ has an ``entropic'' form,
where images are upweighted (relative to a uniform prior) if the pixel
intensities have a low dynamic range. The prior density is
\begin{eqnarray}
p(\boldsymbol{m} | \lambda) \propto \exp
\left[
-\lambda \sum_{i=1}^n m_i \ln m_i
\right]
\end{eqnarray}
where $\lambda$ is a hyperparameter.
In the 1980s, this prior was thought to have a fundamental status, but this
is no longer the case \citep{massinf}. Instead, we can consider the configurational
entropy $-\sum_{i=1}^n m_i \ln m_i$ as simply a function of an image that may
be relevant somehow, and that we are uncertain about.

The posterior for the underlying image given the data is
\begin{eqnarray}
p(\boldsymbol{m} | \boldsymbol{D}, \lambda)
&=& \frac{p(\boldsymbol{m} | \lambda)p(\boldsymbol{D}|\boldsymbol{m}, \lambda)}
{\int p(\boldsymbol{m}|\lambda)p(\boldsymbol{D}|\boldsymbol{m}, \lambda) \,d^n\boldsymbol{m}}\\
&=& \frac{\exp\left[-\lambda \sum_i m_i\ln m_i
-\frac{1}{2\sigma^2}\left(D_i - \sum_{j} P_{ij}m_{j}\right)^2\right]}
{\int \exp\left[-\lambda \sum_i m_i\ln m_i
-\frac{1}{2\sigma^2}\left(D_i - \sum_{j} P_{ij}m_{j}\right)^2\right]\, d^n\boldsymbol{m}}
\end{eqnarray}

This is a `doubly intractable' problem \citep{murray}, since an integral, whose
result is a function of the parameters, appears in the {\em denominator} of the
target density. However, in our case the integral in the
denominator arises from the prior for the parameters, rather than from the
likelihood function.
